Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2014-10-17 Report/kkt_mse_approach.tex
updated draft with KKT distributed schemes

Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other. In this problem, we fix the dual variable \me{\alpha^{(i)}} to a fixed value as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}. At each iteration, the dual variable \me{\alpha^{(i)}} is updated linearly from the earlier value \me{\alpha^{(i-1)}} by a step size of \me{\rho \in [0,1]}. It can be seen that, when the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative thereby forcing the dual variable \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}}, which in turn reduces the transmit precoder weights in \eqref{kkt-mse-4.3}. This reduction in the precoder weights forces the allocated rate of user \me{k} to reduce from the previous iteration as \me{t_k^{(i)} < t_k^{(i-1)}}.

The \ac{KKT} solutions provided in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive precoders \me{\mvec{M}{k,n},\mvec{W}{k,n}} with the single user beamforming and the \ac{MMSE} vectors. The dual variable \me{\alpha}'s corresponding to precoder weights are initialized with ones to provide equal priorities to all streams. Now, the closed form expressions in \eqref{kkt-mse-4} are evaluated sequentially until convergence or to a certain accuracy. In \eqref{kkt-mse-4}, all expressions are in closed form except the transmit precoders \eqref{kkt-mse-4.3}, which depend on the \ac{BS} specific dual variable \me{\delta_b}. It can be solved efficiently by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}. Note that in \eqref{kkt-mse-4}, the fixed \ac{SCA} operating point is given by \me{\tilde{\epsilon}_{l,k,n} = \epsilon_{l,k,n}^{(i-1)}}.

We consider the method proposed in \cite{komulainen2013effective} to design the precoders in a distributed manner across the coordinating \acp{BS} in \me{\mathcal{B}}. Upon receiving the transmitted signal from all \acp{BS} using the updated precoders  \me{\mvec{m}{l,k,n}}, each user update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, the dual variables \me{\lambda_{l,k,n}} and \me{\alpha_{l,k,n}}. Once the dual variable \me{\alpha_{l,k,n}} and the receive beamformers are evaluated, the users will notify it to the coordinating \acp{BS} using precoded uplink pilots with \me{\mvec{\tilde{w}}{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\mvec{w}{l,k,n}} as the precoders. Upon receiving the precoded uplink pilots, each \ac{BS} will use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{w}{l,k,n}^{(i)}} in the expression \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the conjugate of \me{\mbf{x}}. Algorithm \ref{algo-4} outlines the distributed precoder design using the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=1}, \me{\mbf{w}^{(0)}_{l,k,n}} randomly, dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}, and \me{I_{\max}} for certain value}
 \ForEach{\ac{BS} \me{b \in \mc{B}}}{
 initialize \me{i = 0} \;
 \Repeat{until convergence or \me{i \geq I_{\max}}}{
	update \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, and perform downlink transmission \;
	find \me{\mvec{W}{k,n}^{(i)}} using \eqref{kkt-mse-4.6} at each user \;
	evaluate \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at each user with the updated \me{\mvec{W}{k,n}^{(i)}} \;
	using precoded uplink pilots, \me{\mvec{W}{k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} are notified to all \acp{BS} in \me{\mathcal{B}} \;
	\me{i = i + 1} \;
 }
 }
 \caption{\ac{KKT} approach for the \ac{JSFRA} scheme}
 \label{algo-4}
\end{algorithm}

\subsubsection*{Convergence}
The iterative method presented in Algorithm \ref{algo-4} converges to a stationary point at each iteration. Since the \ac{SCA} point \me{\tilde{\epsilon}_{l,k,n}} and the receive beamformers are updated together at each iteration, the convergence proof is not similar to the primal or the \ac{ADMM} methods. The convergence proof can be argued based on the monotonic increase of the objective function at each iteration as follows. The transmit precoders in \eqref{kkt-mse-4.3} improves the objective function after each update following the \ac{SCA} operating point \me{\tilde{\epsilon}_{l,k,n}} update \cite{marks1978technical}. Furthermore, the \ac{MMSE} receivers are globally optimal for the fixed transmit precoders \cite{christensen2008weighted,wmmse_shi}, the alternating beamformer updates improve the objective function monotonically in spite of having a subgradient update in \eqref{kkt-mse-4.1}. It is more suitable for the practical implementation due to the reduction in the signaling overhead and the iterations to converge.
%presented in Algorithm \ref{algo-4} converges to a stationary point if the dual variables \me{\alpha_{l,k,n}} are allowed to converge or for fixed number of iterations \me{J_{\max}}. The convergence of the dual variable is guaranteed, since the problem is convex by fixing the receive beamformers \me{\mvec{w}{l,k,n}} and the operating \ac{MSE} point \me{\epsilon_{l,k,n}} \cite{boyd2011distributed}. Once the dual variables are converged or iterated for certain accuracy, the receivers are updated using the \ac{MMSE} objective. Since the \ac{MMSE} receiver is optimal for the fixed transmit precoders, the objective function will improve or stays the same after the receiver update leading to a monotonic convergence of the iterative algorithm provided in \eqref{kkt-mse-4}.

>>>>

Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other. So, the variable  \me{\alpha^{(i)}} is fixed as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}. At each iteration, the dual variables \me{\alpha^{(i)}} are updated linearly from the earlier \me{\alpha^{(i-1)}} by a step size of \me{\rho \in [0,1]}. When the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative thereby forcing \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}} as in \eqref{kkt-mse-4.1}. Once the \me{\alpha_k^{(i)}} is reduced, the precoder weight in \eqref{kkt-mse-4.3} is lowered to make the rate \me{t_k^{(i)} < t_k^{(i-1)}}.

The \ac{KKT} expressions in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive precoders \me{\mvec{M}{k,n},\mvec{W}{k,n}} with the single user beamforming and the \ac{MMSE} vectors. The dual variable \me{\alpha}'s corresponding to precoder weights are initialized with ones to have equal weights. The transmit precoders in \eqref{kkt-mse-4.3} depends on the \ac{BS} specific dual variable \me{\delta_b}, which can be found by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}. Note that in \eqref{kkt-mse-4}, the fixed \ac{SCA} operating point is given by \me{\tilde{\epsilon}_{l,k,n} = \epsilon_{l,k,n}^{(i-1)}}. Following approaches can be performed to decouple the precoder design problem with the limited signaling between the \acp{BS} in \me{\mathcal{B}}.

As a first approach, in this method, for a fixed the receive beamformers, \me{\alpha_{l,k,n}} and the operating \ac{SCA} point \me{\tilde{\epsilon}_{l,k,n}}, each \ac{BS} evaluates the transmit precoder \me{\mvec{m}{l,k,n}^{(i)}} and exchange the total interference contribution by using the updated precoder to the neighboring \ac{BS} users. On receiving this information, each \ac{BS} will update \eqref{kkt-mse-4.4}, \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2}, and \eqref{kkt-mse-4.1}. For the fixed receive beamformer, the dual variables \me{\alpha_{l,k,n}} and the interference contributions are exchanged until convergence by finding the updated transmit precoders. Once the dual variables are converged, the receivers are updated by performing the downlink transmission. This procedure is iterated until convergence for a fixed \me{I_{\max}} iterations. The convergence is similar to the \ac{JSFRA} scheme with \ac{MSE} reformulation in Section \ref{sec-3.3}.

The following approaches are similar to the decentralization methods proposed in \cite{komulainen2013effective} for the sum rate maximization problem. In the this approach, after receiving the transmitted signal with the recent precoders from all \acp{BS} in \me{\mathcal{B}}, the users evaluate the \ac{MMSE} receiver in \eqref{kkt-mse-4.6} and notify it to the \acp{BS} using the precoded uplink pilots. Upon receiving, each \ac{BS} estimates the \ac{MSE} using \me{\epsilon_{l,k,n}^{(i)} = 1 - \mvec{w}{l,k,n}^{(i)\herm} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)}}. Using the updated \ac{MSE}, \me{t_{l,k,n}^{(i)},\sigma_{l,k,n}^{(i)}}, and \me{\alpha_{l,k,n}^{(i)}} are evaluated using \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1}. The updated dual variables \me{\alpha_{l,k,n}} are exchanged between the \acp{BS} to evaluate the transmit precoders \me{\mvec{m}{l,k,n}^{(i+1)}} for the next iteration.

Finally, in this approach, upon receiving the signal from all \acp{BS}, the users update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\lambda_{l,k,n}} and \me{\alpha_{l,k,n}}. The updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified the \acp{BS} using precoded uplink pilots with \me{\mvec{\tilde{w}}{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\mvec{\bar{w}}{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders. On receiving the precoded uplink pilots, the \acp{BS} will use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{w}{l,k,n}^{(i)}} in \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}. Algorithm \ref{algo-4} outlines the distributed precoder design using the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=1}, \me{\mbf{w}^{(0)}_{l,k,n}, \tilde{\epsilon}_{l,k,n}} randomly, dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}, and \me{I_{\max}} for certain value}
 \ForEach{\ac{BS} \me{b \in \mc{B}}}{
 initialize \me{i = 0} \;
 \Repeat{until convergence or \me{i \geq I_{\max}}}{
	update \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, and perform downlink transmission \;
	find \me{\mvec{W}{k,n}^{(i)}} using \eqref{kkt-mse-4.6} at each user \;
	evaluate \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at each user with the updated \me{\mvec{W}{k,n}^{(i)}} \;
	using precoded uplink pilots, \me{\mvec{W}{k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} are notified to all \acp{BS} in \me{\mathcal{B}} \;
	\me{i = i + 1} \;
 }
 }
 \caption{\ac{KKT} approach for the \ac{JSFRA} scheme}
 \label{algo-4}
\end{algorithm}\vspace{-0.1in}
%\subsubsection*{Convergence}
%The iterative method presented in Algorithm \ref{algo-4} converges to a stationary point at each iteration. Since the \ac{SCA} point \me{\tilde{\epsilon}_{l,k,n}} and the receive beamformers are updated together at each iteration, the convergence proof can be argued based on the monotonic increase in the objective function at each iteration. In order to illustrate the convergence, we adopt the following argument. The transmit precoders in \eqref{kkt-mse-4.3} improves the objective function after each update following the \ac{SCA} operating point \me{\tilde{\epsilon}_{l,k,n}} update \cite{marks1978technical}. Furthermore, the \ac{MMSE} receivers are globally optimal for the fixed transmit precoders \cite{christensen2008weighted,wmmse_shi}, the alternating beamformer updates improve the objective function monotonically in spite of having a subgradient like update in \eqref{kkt-mse-4.1}.
%presented in Algorithm \ref{algo-4} converges to a stationary point if the dual variables \me{\alpha_{l,k,n}} are allowed to converge or for fixed number of iterations \me{J_{\max}}. The convergence of the dual variable is guaranteed, since the problem is convex by fixing the receive beamformers \me{\mvec{w}{l,k,n}} and the operating \ac{MSE} point \me{\epsilon_{l,k,n}} \cite{boyd2011distributed}. Once the dual variables are converged or iterated for certain accuracy, the receivers are updated using the \ac{MMSE} objective. Since the \ac{MMSE} receiver is optimal for the fixed transmit precoders, the objective function will improve or stays the same after the receiver update leading to a monotonic convergence of the iterative algorithm provided in \eqref{kkt-mse-4}.

### 2014-10-17 Report/mse_formulation.tex
updated draft with KKT distributed schemes

Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,n,k}} given the fixed receive beamformers. Once the optimal precoders are obtained, the local \ac{MSE} variable  \me{\tilde{\epsilon}_{l,k,n}} is updated with the current update \me{\epsilon_{l,k,n}}. The optimization problem for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given as
\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-4.3},\, \eqref{eqn-mse-1.3},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
\end{IEEEeqnarray}
\subsubsection*{Convergence}
Following similar approach as in Section \ref{sec-3.2.1}, at each iteration, the \ac{SCA} subproblems converge to a stationary point of the original nonconvex problem. The uniqueness of the precoders are justified if there is no phase ambiguity in the stationary solution. By reorganizing \eqref{eqn-mse-1.3}
\iftoggle{single_column}{
\begin{equation}
\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} + \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
\end{equation}
}{
\begin{multline}
	\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} \\ 
	+ \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
\end{multline}
}
we can see that the ambiguity in the phase rotations for the transmit and the receive beamformers are eliminated by the presence of real component in the \ac{MSE} expression.

At each \ac{SCA} iteration, the transmit precoders are obtained uniquely by minimizing \eqref{eqn-mse-1} due to the convex nature of the relaxed problem. Using the transmit precoders, the receive beamformers are obtained using the \ac{MMSE} receivers. The \ac{MMSE} receiver minimizes the objective value for the fixed transmit precoders, leading to the monotonic convergence of the objective function. At each \ac{SCA} step, the optimal value of the previous iteration is also included in the domain of the problem, and the objective value can either decrease or stays the same after each iteration.

>>>>

Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,n,k}} given the fixed receive beamformers. Once the optimal precoders are obtained, the local \ac{MSE} variable  \me{\tilde{\epsilon}_{l,k,n}} is updated with the current update \me{\epsilon_{l,k,n}}. The optimization problem for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given as
\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-4.3},\, \eqref{eqn-mse-1.3},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
\end{IEEEeqnarray}
\subsubsection*{Convergence}
Following similar approach as in Section \ref{sec-3.2.1}, at each iteration, the \ac{SCA} subproblems converge to a stationary point of the original nonconvex problem. The uniqueness of the precoders are justified if there is no phase ambiguity in the stationary solution. By reorganizing \eqref{eqn-mse-1.3} as
\iftoggle{single_column}{
\begin{equation}
\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} + \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
\end{equation}
}{
\begin{multline}
	\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} \\ 
	+ \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
\end{multline}
}
we can see that the ambiguity in the phase rotations for the transmit and the receive beamformers are eliminated by the presence of real component in the \ac{MSE} expression.

At each \ac{SCA} update, the transmit precoders are obtained uniquely by minimizing \eqref{eqn-mse-1} due to the convex nature of the relaxed problem. For a fixed transmit precoders, the \ac{MMSE} receiver improves the objective value \cite{christensen2008weighted,wmmse_shi}, leading to the monotonic convergence of the objective function. At each \ac{SCA} step, the optimal value of the previous iteration is also included in the domain of the problem, and the objective value can either decrease or stays the same after each iteration. Note that the objective function improves at each iteration, whereas the sum rate need not follow the same behavior.

### 2014-10-17 Report/simulation_results.tex
updated draft with KKT distributed schemes

For a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with the lowest path loss component. Fig. \subref*{fig-1} shows the performances of the centralized schemes for a single receive antenna system. It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRME} schemes to perform the optimal allocations to minimize the total number of backlogged packets. The total number of queued packets for Fig. \subref*{fig-1} is given by \me{Q_k = [14,15,14,8,12,9,12,11,11]} bits and for Fig. \subref*{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.

The performances of the centralized algorithms are compared in terms of the total number of residual bits remaining in the system after each \ac{SCA} update in Fig. \ref{fig-a}. The \ac{Q-WSRM} algorithm is not optimal due to the problem of over-allocation when the number of queued packets is small, as in Fig. \ref{fig-a}. In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over-allocation problem. It can be seen that the \ac{JSFRA} algorithms converge to the optimal point for all formulations proposed in Section \ref{sec-3.2.1}. All the algorithms are Pareto-optimal and provide different performances based on the weights used to find a point in the rate region.

In both scenarios defined in Fig. \ref{fig-a}, \ac{Q-WSRME} performs marginally inferior to the \ac{JSFRA} algorithms due to the weights used in the rate maximization algorithm. The performance degradation can be attributed to the fact that the \ac{Q-WSRME} algorithm favors the users with the large number of backlogged packets as compared to the users with better channel conditions. Fig. \subref*{fig-2} compares the algorithms for \me{N_R = 2} receive antenna case. In all figures, the receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{J_{\max} = 1} in Algorithm \ref{algo-1}. It is also noted that the performance degradation by performing the group update is very minimal. Since the receiver minimizes the objective for the fixed transmit precoders, the convergence is monotonic as can be seen from the figures.

>>>>

For a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with the lowest path loss component. Fig. \subref*{fig-1} shows the performances of the centralized schemes for a single receive antenna system. The total number of queued packets for Fig. \subref*{fig-1} is given by \me{Q_k = [14,15,14,8,12,9,12,11,11]} bits and for Fig. \subref*{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.

The performances of the centralized algorithms are compared in terms of the total number of residual bits remaining in the system after each \ac{SCA} update in Fig. \ref{fig-a}. The \ac{Q-WSRM} algorithm is not optimal due to the problem of over-allocation when the number of queued packets are few in number. In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over-allocation. It can be seen that the \ac{JSFRA} algorithms converge to the optimal point for all formulations proposed in Section \ref{sec-3.2.1}. All the algorithms are Pareto-optimal and provide different performances based on the weights used to find a point in the rate region.

For both scenarios in Fig. \ref{fig-a}, the \ac{Q-WSRME} performs marginally inferior to the \ac{JSFRA} algorithms due to the weights used in the algorithm. The performance loss is  attributed to the fact that the \ac{Q-WSRME} algorithm favors the users with the large number of backlogged packets as compared to the users with better channel conditions. Fig. \subref*{fig-2} compares the algorithms for \me{N_R = 2} receive antenna case. In all figures, the receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{J_{\max} = 1} in Algorithm \ref{algo-1}. It is also noted that the performance degradation by performing the group update is very minimal. Since the receiver minimizes the objective for the fixed transmit precoders, the convergence is monotonic as can be seen from the figures.
